Hierarchical and grouped time series forecasting: an application to Emergency Medical Services

### 2022-10-27 manuscript/03-experiment.qmd
adding the missing img (img/group) and the r code to create incident_gt in the incidents.R script in data

We are interested in generating forecasts to inform the planning horizon of $ph=7 to 42$ days, interested by planners in the ambulance services trust. The forecast horizon in this study is $fh = 2 \times ph$ days ahead (2*42 days planning horizon). This is because the planning is generally freezed for ph days and considering a forecast horizon of ph days might not be helpful for planning. While forecasts are generated for $2 \times ph$ days ahead, performance evaluation is only assessed based on the last $ph$ days and not the $2 \times ph$ days. The forecasts are produced for the holdout of 365 days using time series cross-validation [@hyndman2021forecasting]. 
In the following section, we discuss the dataset, describe the forecasting methods used to generate base forecasts and present the point and probabilistic accuracy measures.

@@

```{r}
#| label: fig-feature
#| cache: true
#| out.width: "70%"
#| fig.align: center
#| fig-cap: "Time series features of attended incidents across all levels (1530 series)"
library(feasts)
incident_gthf <- read_rds(here::here("data/incident_gt.rds"))
incident_gthf %>% 
  features(incidents,feat_stl) %>%
  ggplot(aes(x = trend_strength, y = seasonal_strength_week)) +
  geom_point(pch=1)+
  ggthemes::theme_few()
```

>>>>

We are interested in generating forecasts to inform the planning horizon of $ph= 42$ days, interested by planners in the ambulance services trust. The forecast horizon in this study is $fh = 2 \times ph$ days ahead (2*42 days planning horizon). This is because the planning is generally freezed for $ph$ days and considering a forecast horizon of $ph$ days might not be helpful for planning. While forecasts are generated for $2 \times ph$ days ahead, performance evaluation is only assessed based on the last $ph$ days and not the $2 \times ph$ days. The forecasts are produced for the holdout of 365 days using time series cross-validation [@hyndman2021forecasting]. 
In the following section, we discuss the dataset, describe the forecasting methods used to generate base forecasts and present the point and probabilistic accuracy measures.

@@

```{r}
#| label: fig-feature
#| cache: true
#| out.width: "70%"
#| fig.align: center
#| fig-cap: "Time series features of attended incidents across all levels (1530 series)"
library(feasts)

incident_gthf <- read_rds(here::here("data/incident_gt.rds"))
incident_gthf %>% 
  features(incidents,feat_stl) %>%
  ggplot(aes(x = trend_strength, y = seasonal_strength_week)) +
  geom_point(pch=1)+
  ggthemes::theme_few()
```
